\chapter{Introduction}

During my last year of studies at the University of Technology of Belfort-
Montbeliard (UTBM) in Computer Science Engineering, I acquired the
theoretical fundamentals in computer engineering, more particularly in
Software and Knowledge Engineering. In order to achieve my master in
engineering degree, my curriculum requires a 24-weeks final degree project to
apply and develop my skills in a professional activity.

I have chosen to apply to do this internship at Hindsite Interactive in order to
go into details in the web development and multimedia fields of study, an area
in expansion that interests me more particularly. In addition I wanted to do this
project in a foreign country to continue my international experience initiated
with my ST40 (technical internship) in Basel, Switzerland. The project that
Hindsite offered me was ambitious and required the mastery of a range of
different technologies.

Hindsite Interactive is a small business specialized in multimedia, web
development, web design and website hosting. The main services proposed
are designing, web site creation and an online tool that can be compared to a
Content Management System (CMS) called Easy Web Content (EWC). This
tool allows customers to create a new website, edit an existing one and
manage their sites.

My internship as a junior web developer has for main task to create new add-
ons for EWC and to develop a manager to enable clients to create, customize,
edit and populate these add-ons. An add-on is defined as an interactive
dynamic module that can be embedded in their website by clients. The goal is
to realize a common structure for all add-ons to reduce development time for
further add-ons.

After a presentation of the company and the Easy Web Content site, I will
describe the organization of the internship and finally detail the achieved work.

\clearpage
