\chapter{Introduction}

During my last year of studies at the Mines de Douai in ISIC major, I have to achieve a 24-weeks final degree project to
apply and develop my skills in a professional activity.

I have chosen to apply to do this internship at Hindsite Interactive in order to
go into details in the web development and multimedia fields of study, an area
in expansion that interests me more particularly. In addition I wanted to do this
project in a foreign country as I would learn even more in another culture's environment. The project that
Hindsite offered me was ambitious and required the mastery of a range of
different technologies.

Hindsite Interactive is a small business specialized in multimedia, web
development, web design and website hosting. The main services proposed
are design, web site creation and an online tool that can be compared to a
Content Management System (CMS) called Easy Web Content (EWC). This
tool allows customers to edit and manage their html website.

My internship as a junior web developer had for main task to create a site builder application for Easy Web Content, with which the user will be able to create a new website from scratch. By being able to lead the development part of this project, I was able to further develop project management skills and widen my knowledge in web technologies.

After a presentation of the company and the Easy Web Content site, I will
describe the organization of the internship and finally detail the achieved work.

\clearpage
