\chapter*{Conclusion}

\section*{Overview of the work achieved}

During this internship I learned a lot in web development. I had never done 
Php/Mysql in a professional environment and now it is safe to say that I am pretty 
comfortable with these technologies and the extent of it.
\\I was also able to improve my knowledge in client side language, such as HTML, CSS and 
JavaScript, which I had previously worked with in my previous internship. I also discovered 
and used the JavaScript API jQuery, which is one of the most used and popular API to develop with.

Some of the other fields I was able to discover were Web Services (SOAP), Flash (especially ActionScript), 
working with SVN and Mantis and build tasks (Phing).

I am now staying at Hindsite six other months and will continue developing mainly for the Easy 
Web Content Site Builder. We should soon begin a test phase that will give us an idea of how far 
we are in the project and if we can put down a launch date anytime soon.

\section*{Work and organization}

In the United States the hours of work per week are quite the same than in France (around
40 hours) and I was mostly satisfied with the progression of my work.
I was granted a lot of independence in the choice of technologies, implementation,
methods and organization. I am really glad I was able to start a new project as it involved 
a big part of conception and brainstorming, not only development. I could always give my opinion and submit my ideas, and 
choose which direction to take development-wise.

When I arrived at Hindsite Interactive, there was no project management tool, and I think Hindsite could work on that
to ease the development of new projects. 

For example we do not have any Subversion tool to work with and as we are often 
two people working on shared resources this was always an issue and 
it happens that we lose time because of that.
This is a point that me and previous interns already talked about to Mr. Taei but
because do not have access to the server configuration we cannot configure a SVN
ourselves.
\\Another improvement of organization would be to use a Bug Tracking tool. Right now we are still
using google documents for many of the projects and in those you can't really track the advancement of a project or debug easily.

We had those tools set up for the Easy Web Content Sitebuilder, 
and it would have been really hard to develop this application without them.